---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# tidymodules

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

Shiny modules is a great feature of Shiny as it helps de-complexify app development by introducing reusable building blocks (implemented with namespacing und module functions). The *tidymodules* package is built on top of this functionality to provide a robust structure and a clear convention for shiny modules development. 

Some key features of this package are:

* module encapsulation and semantic reference (R6)
* a clear model for managing inter-module communication
  * input/output ports
  * pipes
  * modules connection network
* a better experience for the module users (no more namespacing, only dealing with one reference)
* the use of object-oriented programming concepts like inheritance to do module abstraction.

## Installation

You can install the most recent version of *tidymodules* from [GitHub](https://github.com/Novartis/tidymodules) with:

``` r
library(devtools)
install_github("Novartis/tidymodules")
```

## Example

This is a basic example which shows you how to use the package

```{r example}
## how to list tidymodules examples
```

To list the available examples use this

```{r}
tidymodules::showExamples()
```

To run an example

``` r
tidymodules::showExamples(3)
```


Please note that the *tidymodules* package is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
